Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-06-29 paper.tex
Fix typo
Split perf curve subplots into their own figures and update since resizing

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}

@@

\begin{document}

\listoftodos

@@

Full performance curves for various Reynolds numbers are plotted in
Figure~\ref{fig:perf-curves}. There is essentially no change in the shape of the
drag coefficient curves---merely an upward shift in $C_D$ with increasing $Re$.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/perf_curves}
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

@@

These same wake maps were taken for $Re_D = 0.4 \time 10^6$, $0.6 \times 10^6$,
$0.8 \times 10^6$, and $1.2 \times 10^6$. Qualitatively, these look strikingly
similar, so they have not been plotted here. We will instead compare and
contrast the wake behavior by examining spectra and wake transport terms in the
equations that govern the downstream evolution.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$, 
$y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

>>>>

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}
\usepackage{lineno}

@@

\begin{document}
%\linenumbers
\listoftodos

@@

Full power and rotor drag coefficient curves for various Reynolds numbers are
plotted in Figure~\ref{fig:cp-curves} and Figure~\ref{fig:cd-curves},
respectively. There is essentially no change in the shape of the drag
coefficient curves---merely an upward shift in $C_D$ with increasing $Re$.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cp_curves}
\caption{Mean power coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cd_curves}
\caption{Mean rotor drag coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:cd-curves}
\end{figure}

@@

These same wake maps were taken for $Re_D = 0.4 \times 10^6$, $0.6 \times 10^6$,
$0.8 \times 10^6$, and $1.2 \times 10^6$. Qualitatively, these look strikingly
similar, so they have not been plotted here. We will instead compare and
contrast the wake behavior by examining spectra and wake transport terms in the
equations that govern the downstream evolution.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.85\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$, 
$y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}
